SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-01-31 paper_rl/neural_network.tex
Changed detail in draw.io illustration
Changes for RL section
Change plots

    \path (a1.east |- a1.south)+(2.5,0.25) node (u1)[anchor=south west]%

@@

\node [input place] (s1) [label={[align=center]left: State (8)}] {};

@@

\node [place] (s10) [below right of=s1, label={[align=center]below: Linear}] {};

@@

\node [place] (s13) [right of=s21, label={[align=center]above: Linear}] {};

@@

\node [place] (s16) [below of=s13, label={[align=center]below: Linear}] {};

>>>>

    \path (a1.east |- a2.north)+(2.5,-0.75) node (u1)[anchor=south west]%

@@

\node [input place] (s1) [label={[align=center]below right: Sample (16)}] {};

@@

\node [place] (s10) at (\shortside,-\shortside-\nodedistance) [label={[align=center]below: Linear}] {};

@@

\node [place] (s16) [right of=s21, label={[align=center]below: Linear}] {};
\node [place] (s13) [above of=s16, label={[align=center]above: Linear}] {};

@@
